Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2021-11-08 Supplemental-Material-B-Annotated-Analysis.Rmd
SI-B re-rendered

The study procedure mirrored the setup of studies one and two, in that it consisted of pre-, daily diary-, and post-measurement. The participants were invited for daily diary measurements twice a day (at 12 pm and 7pm) for 30 days (*median duration* = `r seconds_to_period(median(difftime(dtMedical$clean$ended.daily, dtMedical$clean$created.daily, units = "secs"), na.rm=TRUE)) %>% as.character`, *MAD duration* = `r seconds_to_period(round(mad(difftime(dtMedical$clean$ended.daily, dtMedical$clean$created.daily, units = "secs"), na.rm=TRUE))) %>% as.character`).  General compliance was high (`r format(round(sum(medicalSampleInfo$dailiesN)/(nrow(medicalSampleInfo)*62)*100,2), nsmall=2)`% filled daily diary surveys for 31 days or more NEED TO RE-CHECK THIS). The response rates were approximately equal during mornings (*n* = `r sum(medicalSampleInfo$morningN)`) and afternoons (*n* = `r sum(medicalSampleInfo$afternoonN)`). All key variables in for this study were part of the short daily diary surveys. 
The measurement of intergroup contacts was identical to study two. The participants recorded between `r dtMedicalSupp$medicalContactFreq$SumContactNL[dtMedicalSupp$medicalContactFreq$SumContactNL > 0] %>% min`--`r dtMedicalSupp$medicalContactFreq$SumContactNL %>% max` interactions with Dutch outgroup members
(`r dtMedicalSupp$medicalContactFreq$PercContactNL[dtMedicalSupp$medicalContactFreq$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtMedicalSupp$medicalContactFreq$PercContactNL %>% max %>% round(2) %>% format(nsmall=2)`% of individual daily diary measurements; `r (sum(dtMedicalSupp$medicalContactFreq$SumContactNL) / nrow(dtMedical$full) * 100) %>% round(2) %>% format(nsmall=2)`% of all `r nrow(dtMedical$full)` daily diary responses).

```{r medicalFreqAttCor}
dtMedicalSupp$medicalContactFreq <-
  dtMedicalSupp$medicalContactFreq %>%
  mutate(
    SumContactNL_c = SumContactNL - mean(SumContactNL, na.rm = TRUE),
    SumContactNLAll_c = SumContactNLAll - mean(SumContactNLAll, na.rm = TRUE),
    AvAttitude_c = AvAttitude - mean(AvAttitude, na.rm = TRUE),
    AvQuality_c = AvQuality - mean(AvQuality, na.rm = TRUE)
  )

# correlation panel
pairs.panels.new(
  dtMedicalSupp$medicalContactFreq %>% select(SumContactNL, SumContactNLAll, AvQuality, AvAttitude),
  labels = c(
    "Sum:\nNumer of beeps with Outgroup Contact (NL)",
    "Sum:\nNumber of Outgroup Contacts (NL)",
    "Mean:\nInteraction Quality",
    "Mean:\nOutgroup Attitudes (NL)"
  )
)

# correlation panel with interaction sums winsorized
pairs.panels.new(
  dtMedicalSupp$medicalContactFreq %>% select(WinSumContactNL, WinSumContactNLAll, AvQuality, AvAttitude),
  labels = c(
    "Sum:\nNumer of beeps with Outgroup Contact (NL)\n[Winsorized]",
    "Sum:\nNumber of Outgroup Contacts (NL)\n[Winsorized]",
    "Mean:\nInteraction Quality",
    "Mean:\nOutgroup Attitudes (NL)"
  )
)
```

@@

We tested the most general contact hypothesis in two steps. First, we assessed whether more intergroup interactions were related to to more positive outgroup attitudes. Second, we tested whether a potential positive effect on outgroup attitudes depended on the interaction quality (jointly with the number of interactions). We find no significant correlation between intergroup contact and average outgroup attitudes --- for neither the total number of outgroup interactions (*r* = `r cor(dtMedicalSupp$medicalContactFreq$SumContactNLAll, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, *p* = `r cor.test(dtMedicalSupp$medicalContactFreq$SumContactNLAll, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`) and the number of measurement beeps with an interaction (*r* = `r cor(dtMedicalSupp$medicalContactFreq$SumContactNL, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, *p* = `r cor.test(dtMedicalSupp$medicalContactFreq$SumContactNL, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`). This is to say that within our data, participants with more outgroup interactions did not have significantly more positive or negative outgroup attitudes. This is again consistent with the results we found in the first study but inconsitent with the significant relationship we find in the second study.

@@

# regression
mdlMedical$lmAttFreqQualX <-
  lm(AvAttitude ~ SumContactNL_c * AvQuality_c, data = dtMedicalSupp$medicalContactFreq)

@@

However, we do find a significant correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes (*r* = `r cor(dtMedicalSupp$medicalContactFreq$AvQuality, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, *p* = `r cor.test(dtMedicalSupp$medicalContactFreq$AvQuality, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`). Thus, when considering the number of interactions and average interaction quality jointly in a linear regression, we only find a main effect of average perceived interaction quality on predict outgroup attitudes (*b* = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, *t*(`r mdlMedical$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","t value"] %>% round(2) %>% format(nsmall=2)`, *p* = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlMedical$lmAttFreqQualXEta %>% filter(Parameter == "AvQuality_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`). Given the missing aggregate relationship between number of interactions and outgroup attitudes, we find no significant effect of interactions themselves nor do we find a significant interaction effect. This result mirrors that of study one but is inconsistent with the second study. But again this inconsistency is not necessarily surprising given that the variables aggregate all within person variation and there were substantially more measurements where participants did not have an interaction (but reported their outgroup attitudes) than measurements that followed an outgroup contact.

@@

(
  mdlMedical$predPltSlopesAttType <-
    ggplot(data = mdlMedical$predSlopesAttType %>% filter(PID %in% dtMedicalSupp$medicalPltIDs), 
           aes(x = TIDnum, y = measure)) +
    geom_line(alpha = 1, color = "blue") +
    geom_line(aes(y = AttitudesDutch), alpha = 1) +
    facet_wrap(~ PID, ncol = 6) +
    xlab("Time") +
    ylab("Outgroup Attitudes") +
    theme_Publication()
)
ggsave(
  filename = "Figures/Medical_PredictionPlot_SlopesAttType.png",
  mdlMedical$predPltSlopesAttType,
  width = 18,
  height = 12,
  dpi = 800,
  units = "cm",
  device = "png"
)
```

@@

# Create and save Model
mdlMedicalOut$Att$lmerNull <-
  lme4::lmer(AttitudesDutch ~ 1 + (1 | PID),
             data = dtMedicalSupp$medicalOutWithinBetween) # use optim if it does not converge
mdlMedicalOut$Att$lmeNull <-
  lme(
    AttitudesDutch ~ 1,
    random = ~ 1 | PID,
    data = dtMedicalSupp$medicalOutWithinBetween,
    na.action = na.omit,
    control = list(opt = "nlmimb")
  ) # use optim if it does not converge

@@

```{r medicalOutModelInterceptAttAllport}
# Create and save Model
mdlMedicalOut$Att$lmeInterceptAllport <-
  lme(
    AttitudesDutch ~ AllportsCondition_cwc,
    random = ~ 1 | PID,
    na.action = na.omit,
    data = dtMedicalSupp$medicalOutWithinBetween
  )

# Get summary with p-values (Satterthwaite's method)
summ(
  mdlMedicalOut$Att$lmerInterceptAllport <-
    lmer(
      AttitudesDutch ~ AllportsCondition_cwc + (1 | PID),
      data = dtMedicalSupp$medicalOutWithinBetween
    ),
  confint = TRUE,
  digits = 3,
  center = FALSE
)

@@

```{r medicalOutModelSlopesAttAllport}
# Create and save Model (optimizer needed to reach convergence)
mdlMedicalOut$Att$lmeSlopesAllport <-
  lme(
    AttitudesDutch ~
      AllportsCondition_cwc,
    random = ~ 1 + AllportsCondition_cwc | PID,
    na.action = na.omit,
    control = lmeControl(opt = "optim"),
    data = dtMedicalSupp$medicalOutWithinBetween
  )

# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
summ(
  mdlMedicalOut$Att$lmerSlopesAllport <- lmer(
    AttitudesDutch ~
      AllportsCondition_cwc +
      (1 + AllportsCondition_cwc | PID),
    data = dtMedicalSupp$medicalOutWithinBetween
  ),
  confint = TRUE,
  digits = 3,
  center = FALSE
)

# all variables standardized within PPT
summ(
  mdlMedicalOut$Att$lmerSlopesAllportZ <- lmer(
    AttitudesDutch_zwc ~
      AllportsCondition_zwc +
      (1 + AllportsCondition_zwc | PID),
    data = dtMedicalSupp$medicalOutWithinBetween
  ),
  confint = TRUE,
  digits = 3,
  center = FALSE
)

@@

# Plot prediction model
mdlMedicalOut$Att$predSlopesAllport <- 
  dtMedicalSupp$medicalOutWithinBetween %>% 
  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
  select(AttitudesDutch, TIDnum, PID) %>% 
  mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesAllport,
                           dtMedicalSupp$medicalOutWithinBetween %>% filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
                           re.form = NA
                           )
         )

@@

```{r medicalOutModelMLQltNull}
# Create and save Model
mdlMedicalOut$Qlt$lmerNull <-
  lme4::lmer(qualityOverall ~ 1 + (1 | PID), 
             data = dtMedicalSupp$medicalOutWithinBetween) # use optim if it does not converge
mdlMedicalOut$Qlt$lmeNull <-
  mdlMedicalOut$Qlt$lmeNull <-lme(
    qualityOverall ~ 1,
    random = ~ 1 | PID,
    na.action = na.omit,
    data = dtMedicalSupp$medicalOutWithinBetween,
    control = list(opt = "nlmimb")
  ) # use optim if it does not converge

@@

```{r medicalOutModelInterceptQltAllport}
# Create and save Model
mdlMedicalOut$Qlt$lmeInterceptAllport <-
  lme(
    qualityOverall ~ AllportsCondition_cwc,
    random = ~ 1 | PID,
    na.action = na.omit,
    data = dtMedicalSupp$medicalOutWithinBetween
  )

# Get summary with p-values (Satterthwaite's method)
summ(
  mdlMedicalOut$Qlt$lmerInterceptAllport <-
    lmer(
      qualityOverall ~ AllportsCondition_cwc + (1 | PID),
      data = dtMedicalSupp$medicalOutWithinBetween
    ),
  confint = TRUE,
  digits = 3,
  center = FALSE
)

@@

```{r medicalOutModelSlopesQltAllport}
# Create and save Model (optimizer needed to reach convergence)
mdlMedicalOut$Qlt$lmeSlopesAllport <-
  lme(
    qualityOverall ~
      AllportsCondition_cwc,
    random = ~ 1 + AllportsCondition_cwc | PID,
    na.action = na.omit,
    control = lmeControl(opt = "optim"),
    data = dtMedicalSupp$medicalOutWithinBetween
  )

# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
summ(
  mdlMedicalOut$Qlt$lmerSlopesAllport <-
    lmer(
      qualityOverall ~
        AllportsCondition_cwc +
        (1 + AllportsCondition_cwc | PID),
      data = dtMedicalSupp$medicalOutWithinBetween
    ),
  confint = TRUE,
  digits = 3,
  center = FALSE
)

@@

# Plot prediction model
mdlMedicalOut$Qlt$predSlopesAllport <- 
  dtMedicalSupp$medicalOutWithinBetween %>%
  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
  select(AttitudesDutch, TIDnum, PID) %>% 
  mutate(measure = predict(mdlMedicalOut$Qlt$lmeSlopesAllport,
                           dtMedicalSupp$medicalOutWithinBetween %>% filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
                           re.form = NA
                           )
         )

(
  mdlMedicalOut$Qlt$predPltSlopesAllport <-
    ggplot(data = mdlMedicalOut$Qlt$predSlopesAllport %>% filter(PID %in% dtMedicalSupp$medicalOutPltIDs), 
           aes(x = TIDnum, y = measure)) +
    geom_line(alpha = 1, color = "blue") +
    geom_line(aes(y = AttitudesDutch), alpha = 1) +
    facet_wrap(~ PID, ncol = 6) +
    xlab("Time") +
    ylab("Outgroup Attitudes") +
    theme_Publication()
)
ggsave(
  filename = "Figures/MedicalOut_PredictionPlot_SlopesAllport.png",
  mdlMedicalOut$Qlt$predPltSlopesAllport,
  width = 18,
  height = 12,
  dpi = 800,
  units = "cm",
  device = "png"
)

@@

```{r medicalOutModelInterceptAttAllportQlt}
# Create and save Model
mdlMedicalOut$Att$lmeInterceptAllportQlt <-
  lme(
    AttitudesDutch ~ AllportsCondition_cwc + qualityOverall_cwc,
    random = ~ 1 | PID,
    na.action = na.omit,
    data = dtMedicalSupp$medicalOutWithinBetween
  )

# Get summary with p-values (Satterthwaite's method)
summ(
  mdlMedicalOut$Att$lmerInterceptAllportQlt <-
    lmer(
      AttitudesDutch ~ AllportsCondition_cwc + qualityOverall_cwc + (1 | PID),
      data = dtMedicalSupp$medicalOutWithinBetween
    ),
  confint = TRUE,
  digits = 3
)

@@

```{r medicalOutModelSlopesAttAllportQlt}
# Create and save Model (optimizer needed to reach convergence)
mdlMedicalOut$Att$lmeSlopesAllportQlt <-
  lme(
    AttitudesDutch ~
      AllportsCondition_cwc + qualityOverall_cwc,
    random = ~ 1 + AllportsCondition_cwc + qualityOverall_cwc | PID,
    na.action = na.omit,
    control = lmeControl(opt = "optim"),
    data = dtMedicalSupp$medicalOutWithinBetween
  )

# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
summ(
  mdlMedicalOut$Att$lmerSlopesAllportQlt <- lmer(
    AttitudesDutch ~
      AllportsCondition_cwc + qualityOverall_cwc +
      (1 + AllportsCondition_cwc + qualityOverall_cwc | PID),
    data = dtMedicalSupp$medicalOutWithinBetween,
    control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
  ),
  confint = TRUE,
  digits = 3
)

@@

# Plot prediction model
mdlMedicalOut$Att$predSlopesAllportQlt <- 
  dtMedicalSupp$medicalOutWithinBetween %>% 
  filter(complete.cases(AllportsCondition, qualityOverall)) %>%
  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
  select(AttitudesDutch, TIDnum, PID) %>% 
  mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesAllportQlt,
                           dtMedicalSupp$medicalOutWithinBetween %>% 
                             filter(complete.cases(AllportsCondition, qualityOverall)) %>%
                             filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
                           re.form = NA
                           )
         )

@@

```{r medicalOutModelInterceptAttCore}
# Create and save Model
mdlMedicalOut$Att$lmeInterceptCore <-
  lme(
    AttitudesDutch ~ KeyNeedFulfillment_cwc,
    random = ~ 1 | PID,
    na.action = na.omit,
    data = dtMedicalSupp$medicalOutWithinBetween
  )

# Get summary with p-values (Satterthwaite's method)
summ(
  mdlMedicalOut$Att$lmerInterceptCore <-
    lmer(
      AttitudesDutch ~ KeyNeedFulfillment_cwc + (1 | PID),
      data = dtMedicalSupp$medicalOutWithinBetween
    ),
  confint = TRUE,
  digits = 3,
  center = FALSE
)

@@

```{r medicalOutModelSlopesAttCore}
# Create and save Model (optimizer needed to reach convergence)
mdlMedicalOut$Att$lmeSlopesCore <-
  lme(
    AttitudesDutch ~
      KeyNeedFulfillment_cwc,
    random = ~ 1 + KeyNeedFulfillment_cwc | PID,
    na.action = na.omit,
    control = lmeControl(opt = "optim"),
    data = dtMedicalSupp$medicalOutWithinBetween
  )

# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
summ(
  mdlMedicalOut$Att$lmerSlopesCore <- lmer(
    AttitudesDutch ~
      KeyNeedFulfillment_cwc +
      (1 + KeyNeedFulfillment_cwc | PID),
    data = dtMedicalSupp$medicalOutWithinBetween
  ),
  confint = TRUE,
  digits = 3,
  center = FALSE
)

# all variables standardized within PPT
summ(
  mdlMedicalOut$Att$lmerSlopesCoreZ <- lmer(
    AttitudesDutch_zwc ~
      KeyNeedFulfillment_zwc +
      (1 + KeyNeedFulfillment_zwc | PID),
    data = dtMedicalSupp$medicalOutWithinBetween
  ),
  confint = TRUE,
  digits = 3,
  center = FALSE
)

>>>>

The study procedure mirrored the setup of studies one and two, in that it consisted of pre-, daily diary-, and post-measurement. The participants were invited for daily diary measurements twice a day (at 12 pm and 7pm) for 30 days (*median duration* = `r seconds_to_period(median(difftime(dtMedical$clean$ended.daily, dtMedical$clean$created.daily, units = "secs"), na.rm=TRUE)) %>% as.character`, *MAD duration* = `r seconds_to_period(round(mad(difftime(dtMedical$clean$ended.daily, dtMedical$clean$created.daily, units = "secs"), na.rm=TRUE))) %>% as.character`).  General compliance was high (`r format(round(sum(medicalSampleInfo$dailiesN)/(nrow(medicalSampleInfo)*62)*100,2), nsmall=2)`% filled daily diary surveys for 31 days or more NEED TO RE-CHECK THIS). The response rates were approximately equal during mornings (*n* = `r sum(medicalSampleInfo$morningN)`) and afternoons (*n* = `r sum(medicalSampleInfo$afternoonN)`). All key variables in for this study were part of the short daily diary surveys. 
The measurement of intergroup contacts was identical to study two. The participants recorded between `r medicalContactFreq$SumContactNL[medicalContactFreq$SumContactNL > 0] %>% min`--`r medicalContactFreq$SumContactNL %>% max` interactions with Dutch outgroup members
(`r medicalContactFreq$PercContactNL[medicalContactFreq$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r medicalContactFreq$PercContactNL %>% max %>% round(2) %>% format(nsmall=2)`% of individual daily diary measurements; `r (sum(medicalContactFreq$SumContactNL) / nrow(dtMedical$full) * 100) %>% round(2) %>% format(nsmall=2)`% of all `r nrow(dtMedical$full)` daily diary responses).

```{r medicalFreqAttCor}
medicalContactFreq <-
  medicalContactFreq %>%
  mutate(
    SumContactNL_c = SumContactNL - mean(SumContactNL, na.rm = TRUE),
    SumContactNLAll_c = SumContactNLAll - mean(SumContactNLAll, na.rm = TRUE),
    AvAttitude_c = AvAttitude - mean(AvAttitude, na.rm = TRUE),
    AvQuality_c = AvQuality - mean(AvQuality, na.rm = TRUE)
  )

# correlation panel
pairs.panels.new(
  medicalContactFreq %>% select(SumContactNL, SumContactNLAll, AvQuality, AvAttitude),
  labels = c(
    "Sum:\nNumer of beeps with Outgroup Contact (NL)",
    "Sum:\nNumber of Outgroup Contacts (NL)",
    "Mean:\nInteraction Quality",
    "Mean:\nOutgroup Attitudes (NL)"
  )
)

# correlation panel with interaction sums winsorized
pairs.panels.new(
  medicalContactFreq %>% select(WinSumContactNL, WinSumContactNLAll, AvQuality, AvAttitude),
  labels = c(
    "Sum:\nNumer of beeps with Outgroup Contact (NL)\n[Winsorized]",
    "Sum:\nNumber of Outgroup Contacts (NL)\n[Winsorized]",
    "Mean:\nInteraction Quality",
    "Mean:\nOutgroup Attitudes (NL)"
  )
)
```

@@

We tested the most general contact hypothesis in two steps. First, we assessed whether more intergroup interactions were related to to more positive outgroup attitudes. Second, we tested whether a potential positive effect on outgroup attitudes depended on the interaction quality (jointly with the number of interactions). We find no significant correlation between intergroup contact and average outgroup attitudes --- for neither the total number of outgroup interactions (*r* = `r cor(medicalContactFreq$SumContactNLAll, medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, *p* = `r cor.test(medicalContactFreq$SumContactNLAll, medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`) and the number of measurement beeps with an interaction (*r* = `r cor(medicalContactFreq$SumContactNL, medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, *p* = `r cor.test(medicalContactFreq$SumContactNL, medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`). This is to say that within our data, participants with more outgroup interactions did not have significantly more positive or negative outgroup attitudes. This is again consistent with the results we found in the first study but inconsitent with the significant relationship we find in the second study.

@@

# regression
mdlMedical$lmAttFreqQualX <-
  lm(AvAttitude ~ SumContactNL_c * AvQuality_c, data = medicalContactFreq)

@@

However, we do find a significant correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes (*r* = `r cor(medicalContactFreq$AvQuality, medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, *p* = `r cor.test(medicalContactFreq$AvQuality, medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`). Thus, when considering the number of interactions and average interaction quality jointly in a linear regression, we only find a main effect of average perceived interaction quality on predict outgroup attitudes (*b* = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, *t*(`r mdlMedical$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","t value"] %>% round(2) %>% format(nsmall=2)`, *p* = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlMedical$lmAttFreqQualXEta %>% filter(Parameter == "AvQuality_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`). Given the missing aggregate relationship between number of interactions and outgroup attitudes, we find no significant effect of interactions themselves nor do we find a significant interaction effect. This result mirrors that of study one but is inconsistent with the second study. But again this inconsistency is not necessarily surprising given that the variables aggregate all within person variation and there were substantially more measurements where participants did not have an interaction (but reported their outgroup attitudes) than measurements that followed an outgroup contact.

@@

(
  mdlMedical$predPltSlopesAttType <-
    ggplot(data = mdlMedical$predSlopesAttType %>% filter(PID %in% medicalPltIDs), 
           aes(x = TIDnum, y = measure)) +
    geom_line(alpha = 1, color = "blue") +
    geom_line(aes(y = AttitudesDutch), alpha = 1) +
    facet_wrap(~ PID, ncol = 6) +
    xlab("Time") +
    ylab("Outgroup Attitudes") +
    theme_Publication()
)
ggsave(
  filename = "Figures/Medical_PredictionPlot_SlopesAttType.png",
  mdlMedical$predPltSlopesAttType,
  width = 18,
  height = 12,
  dpi = 800,
  units = "cm",
  device = "png"
)
```

@@

# Create and save Model
mdlMedicalOut$Att$lmerNull <-
  lme4::lmer(AttitudesDutch ~ 1 + (1 | PID),
             data = medicalOutWithinBetween) # use optim if it does not converge
mdlMedicalOut$Att$lmeNull <-
  lme(
    AttitudesDutch ~ 1,
    random = ~ 1 | PID,
    data = medicalOutWithinBetween,
    na.action = na.omit,
    control = list(opt = "nlmimb")
  ) # use optim if it does not converge

@@

```{r medicalOutModelInterceptAttAllport}
# Create and save Model
mdlMedicalOut$Att$lmeInterceptAllport <-
  lme(
    AttitudesDutch ~ AllportsCondition_cwc,
    random = ~ 1 | PID,
    na.action = na.omit,
    data = medicalOutWithinBetween
  )

# Get summary with p-values (Satterthwaite's method)
summ(
  mdlMedicalOut$Att$lmerInterceptAllport <-
    lmer(
      AttitudesDutch ~ AllportsCondition_cwc + (1 | PID),
      data = medicalOutWithinBetween
    ),
  confint = TRUE,
  digits = 3,
  center = FALSE
)

@@

```{r medicalOutModelSlopesAttAllport}
# Create and save Model (optimizer needed to reach convergence)
mdlMedicalOut$Att$lmeSlopesAllport <-
  lme(
    AttitudesDutch ~
      AllportsCondition_cwc,
    random = ~ 1 + AllportsCondition_cwc | PID,
    na.action = na.omit,
    control = lmeControl(opt = "optim"),
    data = medicalOutWithinBetween
  )

# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
summ(
  mdlMedicalOut$Att$lmerSlopesAllport <- lmer(
    AttitudesDutch ~
      AllportsCondition_cwc +
      (1 + AllportsCondition_cwc | PID),
    data = medicalOutWithinBetween
  ),
  confint = TRUE,
  digits = 3,
  center = FALSE
)

# all variables standardized within PPT
summ(
  mdlMedicalOut$Att$lmerSlopesAllportZ <- lmer(
    AttitudesDutch_zwc ~
      AllportsCondition_zwc +
      (1 + AllportsCondition_zwc | PID),
    data = medicalOutWithinBetween
  ),
  confint = TRUE,
  digits = 3,
  center = FALSE
)

@@

# Plot prediction model
mdlMedicalOut$Att$predSlopesAllport <- 
  medicalOutWithinBetween %>% 
  filter(PID %in% medicalOutPltIDs) %>%
  select(AttitudesDutch, TIDnum, PID) %>% 
  mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesAllport,
                           medicalOutWithinBetween %>% filter(PID %in% medicalOutPltIDs),
                           re.form = NA
                           )
         )

@@

```{r medicalOutModelMLQltNull}
# Create and save Model
mdlMedicalOut$Qlt$lmerNull <-
  lme4::lmer(qualityOverall ~ 1 + (1 | PID), 
             data = medicalOutWithinBetween) # use optim if it does not converge
mdlMedicalOut$Qlt$lmeNull <-
  mdlMedicalOut$Qlt$lmeNull <-lme(
    qualityOverall ~ 1,
    random = ~ 1 | PID,
    na.action = na.omit,
    data = medicalOutWithinBetween,
    control = list(opt = "nlmimb")
  ) # use optim if it does not converge

@@

```{r medicalOutModelInterceptQltAllport}
# Create and save Model
mdlMedicalOut$Qlt$lmeInterceptAllport <-
  lme(
    qualityOverall ~ AllportsCondition_cwc,
    random = ~ 1 | PID,
    na.action = na.omit,
    data = medicalOutWithinBetween
  )

# Get summary with p-values (Satterthwaite's method)
summ(
  mdlMedicalOut$Qlt$lmerInterceptAllport <-
    lmer(
      qualityOverall ~ AllportsCondition_cwc + (1 | PID),
      data = medicalOutWithinBetween
    ),
  confint = TRUE,
  digits = 3,
  center = FALSE
)

@@

```{r medicalOutModelSlopesQltAllport}
# Create and save Model (optimizer needed to reach convergence)
mdlMedicalOut$Qlt$lmeSlopesAllport <-
  lme(
    qualityOverall ~
      AllportsCondition_cwc,
    random = ~ 1 + AllportsCondition_cwc | PID,
    na.action = na.omit,
    control = lmeControl(opt = "optim"),
    data = medicalOutWithinBetween
  )

# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
summ(
  mdlMedicalOut$Qlt$lmerSlopesAllport <-
    lmer(
      qualityOverall ~
        AllportsCondition_cwc +
        (1 + AllportsCondition_cwc | PID),
      data = medicalOutWithinBetween
    ),
  confint = TRUE,
  digits = 3,
  center = FALSE
)

@@

# Plot prediction model
mdlMedicalOut$Qlt$predSlopesAllport <- 
  medicalOutWithinBetween %>%
  filter(PID %in% medicalOutPltIDs) %>%
  select(AttitudesDutch, TIDnum, PID) %>% 
  mutate(measure = predict(mdlMedicalOut$Qlt$lmeSlopesAllport,
                           medicalOutWithinBetween %>% filter(PID %in% medicalOutPltIDs),
                           re.form = NA
                           )
         )

(
  mdlMedicalOut$Qlt$predPltSlopesAllport <-
    ggplot(data = mdlMedicalOut$Qlt$predSlopesAllport %>% filter(PID %in% medicalOutPltIDs), 
           aes(x = TIDnum, y = measure)) +
    geom_line(alpha = 1, color = "blue") +
    geom_line(aes(y = AttitudesDutch), alpha = 1) +
    facet_wrap(~ PID, ncol = 6) +
    xlab("Time") +
    ylab("Outgroup Attitudes") +
    theme_Publication()
)
ggsave(
  filename = "Figures/MedicalOut_PredictionPlot_SlopesAllport.png",
  mdlMedicalOut$Qlt$predPltSlopesAllport,
  width = 18,
  height = 12,
  dpi = 800,
  units = "cm",
  device = "png"
)

@@

```{r medicalOutModelInterceptAttAllportQlt}
# Create and save Model
mdlMedicalOut$Att$lmeInterceptAllportQlt <-
  lme(
    AttitudesDutch ~ AllportsCondition_cwc + qualityOverall_cwc,
    random = ~ 1 | PID,
    na.action = na.omit,
    data = medicalOutWithinBetween
  )

# Get summary with p-values (Satterthwaite's method)
summ(
  mdlMedicalOut$Att$lmerInterceptAllportQlt <-
    lmer(
      AttitudesDutch ~ AllportsCondition_cwc + qualityOverall_cwc + (1 | PID),
      data = medicalOutWithinBetween
    ),
  confint = TRUE,
  digits = 3
)

@@

```{r medicalOutModelSlopesAttAllportQlt}
# Create and save Model (optimizer needed to reach convergence)
mdlMedicalOut$Att$lmeSlopesAllportQlt <-
  lme(
    AttitudesDutch ~
      AllportsCondition_cwc + qualityOverall_cwc,
    random = ~ 1 + AllportsCondition_cwc + qualityOverall_cwc | PID,
    na.action = na.omit,
    control = lmeControl(opt = "optim"),
    data = medicalOutWithinBetween
  )

# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
summ(
  mdlMedicalOut$Att$lmerSlopesAllportQlt <- lmer(
    AttitudesDutch ~
      AllportsCondition_cwc + qualityOverall_cwc +
      (1 + AllportsCondition_cwc + qualityOverall_cwc | PID),
    data = medicalOutWithinBetween,
    control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
  ),
  confint = TRUE,
  digits = 3
)

@@

# Plot prediction model
mdlMedicalOut$Att$predSlopesAllportQlt <- 
  medicalOutWithinBetween %>% 
  filter(complete.cases(AllportsCondition, qualityOverall)) %>%
  filter(PID %in% medicalOutPltIDs) %>%
  select(AttitudesDutch, TIDnum, PID) %>% 
  mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesAllportQlt,
                           medicalOutWithinBetween %>% 
                             filter(complete.cases(AllportsCondition, qualityOverall)) %>%
                             filter(PID %in% medicalOutPltIDs),
                           re.form = NA
                           )
         )

@@

```{r medicalOutModelInterceptAttCore}
# Create and save Model
mdlMedicalOut$Att$lmeInterceptCore <-
  lme(
    AttitudesDutch ~ KeyNeedFulfillment_cwc,
    random = ~ 1 | PID,
    na.action = na.omit,
    data = medicalOutWithinBetween
  )

# Get summary with p-values (Satterthwaite's method)
summ(
  mdlMedicalOut$Att$lmerInterceptCore <-
    lmer(
      AttitudesDutch ~ KeyNeedFulfillment_cwc + (1 | PID),
      data = medicalOutWithinBetween
    ),
  confint = TRUE,
  digits = 3,
  center = FALSE
)

@@

```{r medicalOutModelSlopesAttCore}
# Create and save Model (optimizer needed to reach convergence)
mdlMedicalOut$Att$lmeSlopesCore <-
  lme(
    AttitudesDutch ~
      KeyNeedFulfillment_cwc,
    random = ~ 1 + KeyNeedFulfillment_cwc | PID,
    na.action = na.omit,
    control = lmeControl(opt = "optim"),
    data = medicalOutWithinBetween
  )

# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
summ(
  mdlMedicalOut$Att$lmerSlopesCore <- lmer(
    AttitudesDutch ~
      KeyNeedFulfillment_cwc +
      (1 + KeyNeedFulfillment_cwc | PID),
    data = medicalOutWithinBetween
  ),
  confint = TRUE,
  digits = 3,
  center = FALSE
)

# all variables standardized within PPT
summ(
  mdlMedicalOut$Att$lmerSlopesCoreZ <- lmer(
    AttitudesDutch_zwc ~
      KeyNeedFulfillment_zwc +
      (1 + KeyNeedFulfillment_zwc | PID),
    data = medicalOutWithinBetween
  ),
  confint = TRUE,
  digits = 3,
  center = FALSE
)
